Structural controllability of ecological networks

### 2018-06-20 paper/manuscript.Rmd
Controllability model was not sensitive enough
And was spitting that no variable was correlated despite there being a clear correlation. It was because the range of probabilities was very small. So I ended up using a lm with logit link instead of a glm. The species level figure, the text in the results and the table in the Suppporting Information have been updated

The size of the minimum driver node-set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)a). 
We found that the relative size of the minimum driver node-set was not related to any of the independent variables we evaluated. 
Indeed the null model ($n_D \sim 1$) was the most parsimonious candidate model and all variables were relatively unimportant (based on the AICc; Table  \@ref(S-tab:tab-controllability-model-results)). 
The $n_D$ of empirical networks did not differ to that of a null model that roughly preserved the degree distribution and fully preserved the network connectance ($p = `r sprintf('\\num{%s}', format(randomisations_test$interactions$p.value, digits = 2))`$; Figure \@ref(fig:fig-emp-controllability)b). 
However empirical networks had a larger $n_D$ than null models that preserved the interactions but shuffled the direction of control of the empirical network ($p = `r sprintf('\\num{%s}', format(randomisations_test$directions$p.value, digits = 2))`$).

```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Density plot of (a) the relative size of the minimum driver node-set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks. (b) The density distribution of the difference between the relative size of the minimum driver node-set of random networks and that of empirical networks. We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line). The vertical dashed lines indicate the median values of each distribution."}
drake::loadd(fig_emp_controllability)

g <- fig_emp_controllability %>%
  purrr::map(ggplot2::ggplotGrob)
gb <- rbind(g[[1]], g[[2]], size = "first")
gb$widths <- grid::unit.pmax(g[[1]]$widths, g[[2]]$widths)
grid::grid.newpage()
grid::grid.draw(gb)
```

>>>>

The size of the minimum driver node-set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`). 
We found that the relative size of the minimum driver node-set of invaded communities was not significantly different to that of communities that have not been invaded (Figure \@ref(fig:fig-emp-controllability)a). 
However there was an important negative relationship between $n_D$ and the network asymetry (Figure \@ref(fig:fig-emp-controllability)b). 
Furthermore, there were also negative, albeit weaker, correlations between $n_D$ and connectance, nestedness and species richness (Table  \@ref(S-tab:tab-controllability-model-results)). 
The $n_D$ of empirical networks did not differ to that of a null model that roughly preserved the degree distribution and fully preserved the network connectance ($p = `r sprintf('\\num{%s}', format(randomisations_test$interactions$p.value, digits = 2))`$; Figure \@ref(fig:fig-emp-controllability)b). 
However empirical networks had a larger $n_D$ than null models that preserved the interactions but shuffled the direction of control of the empirical network ($p = `r sprintf('\\num{%s}', format(randomisations_test$directions$p.value, digits = 2))`$).

```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]*1.5, fig.cap="Density plot of (a) the relative size of the minimum driver node-set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks. (b) The density distribution of the difference between the relative size of the minimum driver node-set of random networks and that of empirical networks. We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line). The vertical dashed lines indicate the median values of each distribution."}
drake::loadd(fig_emp_controllability)

cowplot::plot_grid(plotlist = fig_emp_controllability, 
                   ncol = 1, 
                   align = "v")
```

### 2018-06-20 paper/supp-info.Rmd
Controllability model was not sensitive enough
And was spitting that no variable was correlated despite there being a clear correlation. It was because the range of probabilities was very small. So I ended up using a lm with logit link instead of a glm. The species level figure, the text in the results and the table in the Suppporting Information have been updated

replace_terms <- function(x){
  x %>% 
    stringr::str_replace("inv", "inv") %>%
    stringr::str_replace("connectance", "C") %>%
    stringr::str_replace("weighted_NODF", "NODF") %>%
    stringr::str_replace("n_sp", "n_s") %>%
    stringr::str_replace("web_asymmetry", "AS_n") %>%
    stringr::str_replace("interaction_strength_asymmetry", "AS_s") %>%
    stringr::str_replace(stringr::fixed("~"), "\\sim ")
}

AICcmodavg::aictab(controllability_models) %>% 
  dplyr::mutate(Modnames = replace_terms(Modnames)) %>% 
  dplyr::select(Modnames, AICc, Delta_AICc, Cum.Wt) %>%
  dplyr::filter(Delta_AICc <= 8) %>%
  dplyr::rename(model = Modnames, `$\\Delta AICc$` = Delta_AICc, `$AICc$` = AICc, `Cum. Weight` = Cum.Wt) %>%
  dplyr::mutate(model = paste0("$", model, "$")) %>% 
  knitr::kable("latex", 
               escape = FALSE, 
               booktabs = TRUE, 
               digits = 2, 
               linesep = c(""),
               caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks. There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$). Only candidate models with $\\Delta AIC < 8$ are shown.") %>%
  kableExtra::kable_styling(font_size = 8)
```

>>>>

replace_terms <- function(x){
  x %>% 
    stringr::str_replace("inv", "inv") %>%
    stringr::str_replace("connectance", "C") %>%
    stringr::str_replace("weighted_NODF", "NODF") %>%
    stringr::str_replace("n_sp", "$n_s$") %>%
    stringr::str_replace("web_asymmetry", "$AS_n$") %>%
    stringr::str_replace("interaction_strength_asymmetry", "$AS_s$") %>%
    stringr::str_replace(stringr::fixed("~"), "\\sim ")
}

c_mod_table <- MuMIn::model.sel(controllability_models) %>%
  dplyr::filter(weight > 0.01) %>%
  dplyr::select(-logLik, - AICc)

names(c_mod_table) <- replace_terms(names(c_mod_table))

c_mod_table %>% 
  dplyr::mutate(weight = round(weight, 2)) %>%
  knitr::kable("latex", 
               escape = FALSE, 
               booktabs = TRUE, 
               digits = 2, 
               linesep = c(""),
               caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks. There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$). Only candidate models with $\\Delta AIC < 8$ are shown.") %>%
  kableExtra::kable_styling(font_size = 8)
```
